Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-10-03 manuscript/Chapter3-manuscript.Rmd
update dhmlm and manuscript

We analyzed the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`). Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(round(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, the predator's experience was defined as the number of matches played within the study period.

@@

### Software and computer components

All our statistical analyses were performed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster provided by the Digital Research Alliance of Canada. Cedar runs CentOS Linux 7 as an operating system,

cmdstan-2.28.2 cmdstanr_0.4.0 brms 2.16.3

@@

>>>>

We analyzed the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`). Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(round(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the 10^th match would have a value of 9.

@@

### Software and computer specifications

All our statistical analyses were conducted on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster provided by the Digital Research Alliance of Canada. The operating system for Cedar is CentOS Linux 7. The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo sampling with the package "brms" version 2.16.3 [@Burkner2017], and "cmdstanr" version 0.4.0 [@Gabry2021] as the backend for estimation (cmdstan installation version 2.28.2).

@@

We estimated the relationship between hunting success and experience using a Bayesian generalized additive mixed model with thin plate regression splines. Because a maximum of four prey can be captured, we used the beta-binomial family distribution to estimate the success of predators while controlling for overdispersion. The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link. The model had the following form :

\[
\begin{align}
logit (P_{ij}) &= (\beta_{0} + id_{0,i} + \phi_{0,ij}) \\
&\text{ } + \text{ } \beta_{1} \textit{time}_{i} \\
&\text{ } + \text{ } f(\textit{cumul. xp}_{i}) \\
\end{align}
\tag{1}
\]

The number of knots was set to 10.
